\mytitle

### 2021-12-20 paper.tex
rename sections
rename section
extend summary

\section{Comparison of implementation strategies}
\label{sec:toymodel}

@@

\section{An ILP-aware method for the real dilogarithm}
\label{sec:algorithm}

@@

\section{Conclusions}

In this paper different approaches for the numerical calculation of
the real dilogarithm have been compared w.r.t.\ their potential for
the use of instruction\-/level parallelism.  A particular
implementation of a rational minimax approximant has been proposed and
compared to several existing implementations w.r.t.\ runtime.  A C
implementations of the presented algorithm can be found in the
appendix.  C++ and FORTRAN implementations can be found in the
Polylogarithm library \cite{polylogarithm}.  Implementations in Julia
and Rust can be found in \cite{PolyLog.jl} and \cite{polylog},
respectively.

>>>>

\section{Implementation strategies}
\label{sec:toymodel}

@@

\section{ILP-aware approximation of the real dilogarithm}
\label{sec:algorithm}

@@

\section{Summary}

In this paper different approaches for the numerical calculation of
the real dilogarithm have been compared w.r.t.\ their potential for
the use of instruction\-/level (ILP) parallelism.  We found that a
rational minimax approximant in combination with Estrin's scheme to
evaluate the numerator/denominator polynomials provides both a
sufficient numerical precision and a high degree of ILP, potentially
leading to a reduced runtime.  A particular implementation of a
rational minimax approximant has been proposed and compared to several
existing implementations w.r.t.\ runtime.  A C implementations of the
presented algorithm can be found in the appendix.  C++ and FORTRAN
implementations can be found in the Polylogarithm library
\cite{polylogarithm}.  Implementations in Julia and Rust can be found
in \cite{PolyLog.jl} and \cite{polylog}, respectively.
